---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdtools)
library(flextable)
```

# Early-life paternal relationships predict adult female survival in wild baboons

> Code is created by David Jansen
> Archie Lab; University of Notre Dame
> david.awam.jansen@gmail.com

All files are in the folder code. The file names are numbered and/or named according to the order of the analysis.

The corresponding author of the paper is Elizabeth Archie (earchie@nd.edu)

The code below uses a lot of data from the babase database (https://papio.biology.duke.edu/babasewiki/).
To get access to the database contact the corresponding author.

A selection of the final datasets are publicly available at https://zenodo.org/records/14590285
The data in the publicly available has been anonymized. The key to getting back to the original names is available up on request.

R packages

This is an overview of all the packages used for the Early-life paternal relationships predict adult female survival in wild baboons paper.

The code in this repository was created by David Jansen

Archie Lab; University of Notre Dame  

david.awam.jansen@gmail.com  

The corresponding author of the paper is Elizabeth Archie (earchie@nd.edu).

```{r, echo = FALSE, results=FALSE}
packages <- c(
    "broom", "broom.mixed", "cowplot", "dbplyr", "doSNOW", "extrafont", 
    "flextable", "foreach", "ftExtra", "ggfortify", "ggtext", "grid", 
    "kableExtra", "lmerTest", "MuMIn", "officer", "parallel", "patchwork", 
    "purrr", "purrrlyr", "ramboseli", "rptR", "RPostgreSQL", "scales", 
    "showtext", "survminer", "survMisc", "survival", "systemfonts", 
    "tidyverse", "zoo"
)

if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
    install.packages(setdiff(packages, rownames(installed.packages())), dependencies = TRUE)
}

invisible(suppressMessages(devtools::install_github("amboseli/ramboseli")))

lapply(packages, function(pkg) {
  suppressWarnings(suppressMessages(require(pkg, character.only = TRUE)))
})
```

```{r, echo = FALSE}
get_citation_text <- function(library) {
    library %>%
        citation() %>%
        capture.output() %>%
        as_tibble(.name_repair = "unique") %>%
        filter(!str_starts(value, "To cite"),
               !str_starts(value, "A BibTeX entry for LaTeX users is"),
               !str_starts(value, "To see these entries in BibTeX format"),
               !str_starts(value, "bibtex=TRUE")
               ) %>%
        pull(value) %>%
        str_c(collapse = " ") %>%
        str_remove("@Manual\\{.*") %>%
        str_remove("@Article\\{.*") %>%
        str_remove("R package version [^,]+,\\s*") %>%
        str_remove("https?://CRAN\\.R-project\\.org/package=[^\\s]+") %>%
        str_remove_all("‘.*options.*’") %>%
        str_remove_all("options\\(citation\\.bibtex\\.max=999\\)") %>%
        str_replace_all("_", "") %>%
        str_squish() %>%
        str_remove("<")  # remove any lingering
}
```

```{r, echo = FALSE}
tibble(library = packages) %>%
    mutate(version = map(.x = library, .f = packageVersion)) %>%
    mutate(reference = map_chr(.x = library, .f = get_citation_text)) %>%
    unnest(cols = c(version)) %>%
    mutate(version = as.character(version)) %>% 
     flextable() %>%
    flextable::width(j = 3, 8.5) %>%
    ftExtra::colformat_md()
```

For your information the following code was used to load and/or install packages into R.

```{r, echo = FALSE, results=FALSE}
packages <- c(
    "broom", "broom.mixed", "cowplot", "dbplyr", "doSNOW", "extrafont", 
    "flextable", "foreach", "ftExtra", "ggfortify", "ggtext", "grid", 
    "kableExtra", "lmerTest", "MuMIn", "officer", "parallel", "patchwork", 
    "purrr", "purrrlyr", "ramboseli", "rptR", "RPostgreSQL", "scales", 
    "showtext", "survminer", "survMisc", "survival", "systemfonts", 
    "tidyverse", "zoo"
)

if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
    install.packages(setdiff(packages, rownames(installed.packages())), dependencies = TRUE)
}

invisible(suppressMessages(devtools::install_github("amboseli/ramboseli")))

lapply(packages, function(pkg) {
  suppressWarnings(suppressMessages(require(pkg, character.only = TRUE)))
})
```

```{r, echo = FALSE, results=FALSE}
packages <- c(
    "broom", "broom.mixed", "cowplot", "dbplyr", "doSNOW", "extrafont", 
    "flextable", "foreach", "ftExtra", "ggfortify", "ggtext", "grid", 
    "kableExtra", "lmerTest", "MuMIn", "officer", "parallel", "patchwork", 
    "purrr", "purrrlyr", "ramboseli", "rptR", "RPostgreSQL", "scales", 
    "showtext", "survminer", "survMisc", "survival", "systemfonts", 
    "tidyverse", "zoo"
)

if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
    install.packages(setdiff(packages, rownames(installed.packages())), dependencies = TRUE)
}

invisible(suppressMessages(devtools::install_github("amboseli/ramboseli")))

lapply(packages, function(pkg) {
  suppressWarnings(suppressMessages(require(pkg, character.only = TRUE)))
})
```

```{r, echo = FALSE}
get_citation_text <- function(library) {
    library %>%
        citation() %>%
        capture.output() %>%
        as_tibble(.name_repair = "unique") %>%
        filter(!str_starts(value, "To cite"),
               !str_starts(value, "A BibTeX entry for LaTeX users is"),
               !str_starts(value, "To see these entries in BibTeX format"),
               !str_starts(value, "bibtex=TRUE")
               ) %>%
        pull(value) %>%
        str_c(collapse = " ") %>%
        str_remove("@Manual\\{.*") %>%
        str_remove("@Article\\{.*") %>%
        str_remove("R package version [^,]+,\\s*") %>%
        str_remove("https?://CRAN\\.R-project\\.org/package=[^\\s]+") %>%
        str_remove_all("‘.*options.*’") %>%
        str_remove_all("options\\(citation\\.bibtex\\.max=999\\)") %>%
        str_replace_all("_", "") %>%
        str_squish() %>%
        str_remove("<")  # remove any lingering
}
```


```{r, echo = FALSE, results=FALSE}
packages <- c(
    "broom", "broom.mixed", "cowplot", "dbplyr", "doSNOW", "extrafont", 
    "flextable", "foreach", "ftExtra", "ggfortify", "ggtext", "grid", 
    "kableExtra", "lmerTest", "MuMIn", "officer", "parallel", "patchwork", 
    "purrr", "purrrlyr", "ramboseli", "rptR", "RPostgreSQL", "scales", 
    "showtext", "survminer", "survMisc", "survival", "systemfonts", 
    "tidyverse", "zoo"
)

if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
    install.packages(setdiff(packages, rownames(installed.packages())), dependencies = TRUE)
}

invisible(suppressMessages(devtools::install_github("amboseli/ramboseli")))

lapply(packages, function(pkg) {
  suppressWarnings(suppressMessages(require(pkg, character.only = TRUE)))
})
```

And here is the code that was used to create the reference table. 
```{r, echo = FALSE, results=FALSE}
get_citation_text <- function(library) {
    library %>%
        citation() %>%
        capture.output() %>%
        ## THere are some lines that need to be removed
        as_tibble(.name_repair = "unique") %>%
        filter(!str_starts(value, "To cite"),
               !str_starts(value, "A BibTeX entry for LaTeX users is"),
               !str_starts(value, "To see these entries in BibTeX format"),
               !str_starts(value, "bibtex=TRUE")
               ) %>%
        pull(value) %>%
        str_c(collapse = " ") %>%
        str_remove("@Manual\\{.*") %>%
        str_remove("@Article\\{.*") %>%
        str_remove("R package version [^,]+,\\s*") %>%
        str_remove("https?://CRAN\\.R-project\\.org/package=[^\\s]+") %>%
        str_remove_all("‘.*options.*’") %>%
        str_remove_all("options\\(citation\\.bibtex\\.max=999\\)") %>%
        str_replace_all("_", "") %>%
        str_squish() %>%
        str_remove("<")  # remove any lingering
}
```

```{r, echo = FALSE, results=FALSE}
tibble(library = packages) %>%
    mutate(version = map(.x = library, .f = packageVersion)) %>%
    mutate(reference = map_chr(.x = library, .f = get_citation_text)) %>%
    unnest(cols = c(version)) %>%
    mutate(version = as.character(version)) %>% 
     flextable() %>%
    flextable::width(j = 3, 8.5) %>%
    ftExtra::colformat_md()
```
